$Z_3$ topological order in the quantum dimer-pentamer model

### 2016-09-10 qdpm_paper.tex
minor paper changes

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{$Z_3$ Gauge theory on the Square Lattice}

Here we will review the string-net implementation of $Z_3$ gauge theory on the square lattice. We define a three -dimensional Hilbert space on each link, corresponding to the presence or absence of an oriented string segment that carries $Z_3$ electric flux which we represent graphically as
\begin{equation}
     \vvemptylink  \rightarrowlink \leftarrowlink
\end{equation}

        In the $Z_3$ toric three degrees of freedom live on each link.
        We can represent the $Z_3$ algebra through the following expressions
        %
        %Z_N
        %\begin{equation}
        %    E |n\rangle = n |n\rangle, ~ n=0,1,2,...,N-1
        %    \\
        %    e^{iA} |n\rangle = |n+1 \rangle, ~ n=0,1,2,...,N-2
        %    \\
        %    e^{iA} |N-1\rangle = |0\rangle
        %    %\label{eqn:}
        %\end{equation}
        %Z_3
        %
        \begin{equation}
            \begin{split}
            & E_l |n_l\rangle = n_l |n_l\rangle, ~ n_l=0,1,2
            \\
            & e^{iA_l} |n_l \rangle = |n_l+1 \rangle, ~ n_l =0,1
            \\ 
            & e^{iA_l} |2 \rangle = |0\rangle
            \end{split}
            ,
            %\label{eqn:}
        \end{equation}
        %
        where the operators $E_l$ and $A_l$ act on a given link $l$ and are analogous to the 
        electric field and vector potential respectively. 
        By assigning orientations to the links between two vertices we can define the three degrees of
        freedom pictorially. 
        %
        % 
        To simplify notation, we define $e^{iA_l}$ as the operator $Q$ which acts on the links in the
        following way
        \begin{equation}
            \begin{split}
                & Q^\dagger_{vv'}  | \vvemptylink \rangle = | \rightarrowlink \rangle
                ,
                \\
                & Q^\dagger_{vv'}  | \rightarrowlink \rangle = | \leftarrowlink \rangle
                ,
                \\
                & Q^\dagger_{vv'}  | \leftarrowlink \rangle = | \emptylink \rangle
                .
            \end{split}
            %\label{eqn:}
        \end{equation}
        The link is specified by the two vertices it connects. The operator
        $Q^\dagger_{vv'}$ acts in the direction from the first subscript to the second subscript, in
        this case denoted as $v$ and $v'$. 
        Changing the direction in which $Q$ operates is equivalent to taking the hermitian conjugate
        of the operator withougt changing the direction.  
        %
        \begin{equation}
            (Q^\dagger_{vv'})^\dagger = Q_{vv'}^\dagger
            .
            %\label{eqn:}
        \end{equation}

@@

%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
    \centering
    \includegraphics[width=1.0\columnwidth]{spatial_cors_end_to_end_parallel.pdf}
    \caption{Correlation function between parallel dimers (end-to-end) on the same (blue) and different (red) 
    sub-lattice for a $L=64$ lattice.}
    \label{fig:spatial_dmr_cor}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

>>>>

    \section{$Z_3$ Toric Code on the Square Lattice}
        In the $Z_3$ toric three degrees of freedom live on each link.
        We can represent the $Z_3$ algebra through the following expressions
        %
        %Z_N
        %\begin{equation}
        %    E |n\rangle = n |n\rangle, ~ n=0,1,2,...,N-1
        %    \\
        %    e^{iA} |n\rangle = |n+1 \rangle, ~ n=0,1,2,...,N-2
        %    \\
        %    e^{iA} |N-1\rangle = |0\rangle
        %    %\label{eqn:}
        %\end{equation}
        %Z_3
        %
        \begin{equation}
            \begin{split}
            & E_l |n_l\rangle = n_l |n_l\rangle, ~ n_l=0,1,2
            \\
            & e^{iA_l} |n_l \rangle = |n_l+1 \rangle, ~ n_l =0,1
            \\ 
            & e^{iA_l} |2 \rangle = |0\rangle
            \end{split}
            ,
            %\label{eqn:}
        \end{equation}
        %
        where the operators $E_l$ and $A_l$ act on a given link $l$ and are analogous to the 
        electric field and vector potential respectively. 
        By assigning orientations to the links between two vertices we can define the three degrees of
        freedom pictorially. 
        %
        \begin{itemize}
            \item $\vvemptylink$ 
            \item $\rightarrowlink$ 
            \item $\leftarrowlink$ 
        \end{itemize}
        % 
        To simplify notation, we define $e^{iA_l}$ as the operator $Q$ which acts on the links in the
        following way
        \begin{equation}
            \begin{split}
                & Q^\dagger_{vv'}  | \vvemptylink \rangle = | \rightarrowlink \rangle
                ,
                \\
                & Q^\dagger_{vv'}  | \rightarrowlink \rangle = | \leftarrowlink \rangle
                ,
                \\
                & Q^\dagger_{vv'}  | \leftarrowlink \rangle = | \emptylink \rangle
                .
            \end{split}
            %\label{eqn:}
        \end{equation}
        The link is specified by the two vertices it connects. The operator
        $Q^\dagger_{vv'}$ acts in the direction from the first subscript to the second subscript, in
        this case denoted as $v$ and $v'$. 
        Changing the direction in which $Q$ operates is equivalent to taking the hermitian conjugate
        of the operator withougt changing the direction.  
        %
        \begin{equation}
            (Q^\dagger_{vv'})^\dagger = Q_{vv'}^\dagger
            .
            %\label{eqn:}
        \end{equation}

@@

%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
    \centering
    \includegraphics[width=1.0\columnwidth]{spatial_cors_perp.pdf}
    \caption{Correlation function between perpendicular dimers on the same (blue) and different (red) 
    sub-lattice for a $L=64$ lattice.}
    \label{fig:spatial_dmr_cor}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
